---
title: "ADHD Adults Diagnosis"
format: 
  html:
    embed-resources: true
editor: visual
execute:
  echo: false
  warning: false
  message: false
---

## ADHD Adults Diagnosis

```{r}

source("setup.R")
source("create_long_data.R")


```



```{r}
#|fig-height: 12
d_ss <- d %>% 
  dplyr::select(
    ID, size, starts_with("sensitivity"), starts_with("specificity"),
    test_description_self
  ) %>%
  dplyr::select(
    ID, size,
    ends_with(
      c("self_report", "neuropsycho_tests", "clinician_interview",
        "combination", "clinician_tool", "clinician_rating", 
        "peer_rating", "neuroimaging", "neuroimaging", 
        "observational", "biomarker", "EEG")
    )
  ) %>%
  dplyr::select(
    !starts_with(c(
      "sensitivity_CI", "specificity_CI", 
      "sensitivity_other", "specificity_other"))
  )

d_test_description_self <- d %>%
  dplyr::select(
    ID, test_description_self
  ) %>% 
  dplyr::distinct()

d_sens <- d_ss %>%
  dplyr::select(ID, starts_with("sens")
  )

d_spec <- d_ss %>%
  dplyr::select(ID, starts_with("spec")
  )

d_sens_long <- d_sens %>%
  tidyr::pivot_longer(
    cols = -ID
  ) %>%
  dplyr::rename(sensitivity = value)%>%
  dplyr::mutate(name = stringr::str_remove(name, "sensitivity_"))



d_spec_long <- d_spec %>%
  tidyr::pivot_longer(
    cols = -ID
  ) %>%
  dplyr::rename(specificity = value) %>%
  dplyr::mutate(name = stringr::str_remove(name, "specificity_"))


d_ss_long <- dplyr::full_join(
  d_sens_long, d_spec_long
) %>% 
  dplyr::filter(
    !is.na(sensitivity) & !is.na(specificity)
  ) %>% 
  dplyr::mutate(
    name = sapply(name, capitalize_first)
  ) %>%
  dplyr::mutate(
    name = stringr::str_replace_all(name, "_", " "),
    name = ifelse(
      name == "Neuropsycho tests", "Neuropsychological Test", name
    ),
    name = ifelse(
      name == "Self report", "Self-Report Questionnaire", name
    ),
    name = ifelse(
      name == "Peer rating", "Peer-Rating", name
    ),
    name = ifelse(
      name == "Clinician interview", "Clinician Tool", name
    ),
    
  )

# mark neurotypicals
d_neurotypical <- d %>% dplyr::select(ID, Neurotypical, size) %>% 
  dplyr::mutate(
    Neurotypical = Neurotypical == "Neurotypical"
  )

d_neurotypical_Only <- d %>% 
  dplyr::mutate(
    Neurotypical_Only = Neurotypical == "Neurotypical" &
      Clinical != "Clinical" &
      Autism != "Autism" &
      Antisocial != "Antisocial" &
      Depression != "Depression" &
      Feigning != "Feigning"
  ) %>% dplyr::select(ID, Neurotypical_Only, size)


# count the number of different types of study
d_name_count <- data.frame(dplyr::bind_rows(
  c(name = "Combination", count = sum(d$Combination == "Combination")),
  c(name = "Biomarker", count = sum(d$Biomarker == "Biomarker")),
  c(name = "Clinician Tool", count = sum(d$Clinician.interview == "Clinician interview")),
  c(name = "EEG", count = sum(d$EEG == "EEG")),
  c(name = "Neuroimaging", count = sum(d$Neuroimaging == "Neuroimaging")),
  c(name = "Neuropsychological Test",   count = sum(d$Neuropsychological == "Neuropsychological")),
  c(name = "Peer-Rating",   count = sum(d$Peer.report == "Peer report")),
  c(name = "Self-Report Questionnaire",   count = sum(d$Self.report == "Self report"))
))

# merge with long data
d_ss_long <- d_ss_long %>%
  dplyr::full_join(
    d_neurotypical
  ) %>% 
  dplyr::full_join(
    d_neurotypical_Only
  ) %>% 
  dplyr::filter(!is.na(name))

ggplot2::ggplot(
  d_ss_long, 
  aes(
    x = sensitivity, 
    y = specificity)) +
  geom_point() +
  xlab("Sensitivity (%)") + 
  ylab("Specificity (%)") +
  xlim(c(0, 100)) + 
  ylim(c(0, 100))


d_ss_long <- d_ss_long %>%
  dplyr::full_join(d_name_count, by = "name") %>%
  dplyr::mutate(
    name_with_count = paste0(name, " (n = ", count, " studies)")
  )

ggplot2::ggplot(
  d_ss_long, 
  aes(
    x = sensitivity, 
    y = specificity,
    colour = name, shape = Neurotypical)) +
  geom_point(size = 2.5) +
  xlab("Sensitivity (%)") + 
  ylab("Specificity (%)") +
  facet_wrap(~ name_with_count) +
  guides(colour = "none") +
  theme(legend.position = "bottom") +
  xlim(c(0, 100)) + 
  ylim(c(0, 100))
```

```{r}

#Figure 8
ggplot2::ggplot(
  d_ss_long, 
  aes(
    x = sensitivity, 
    y = specificity,
    colour = name, shape = Neurotypical_Only)) +
  geom_point(size = 2.5) +
  xlab("Sensitivity") + 
  ylab("Specificity") +
  facet_wrap(~ name_with_count, nrow = 2) +
  guides(colour = "none") +
  labs(
    shape = "Neurotypical only"
  ) +
  xlim(c(0, 100)) + 
  ylim(c(0, 100))

# separate charts
for (name_1 in d_ss_long$name) {
  plot <- ggplot2::ggplot(
    d_ss_long %>% dplyr::filter(name_1 == name), 
    aes(
      x = sensitivity, 
      y = specificity,
      shape = Neurotypical_Only)) +
    geom_point(size = 2.5) +
    xlab("Sensitivity") + 
    ylab("Specificity") +
    guides(colour = "none") +
    labs(
      shape = "Neurotypical only"
    ) +
    ggtitle(name_1) +
    xlim(c(0, 100)) + 
    ylim(c(0, 100))
  print(plot)
}


# Figure 8 separate charts

```

Self report only

```{r}

# this is figure 5
cat("self report<p>")
# 1. Prepare your data first
plot_data <- d_ss_long %>%
  dplyr::filter(
    name == "Self-Report Questionnaire"
  ) %>%
  dplyr::inner_join(
    d_test_description_self
  ) %>%
  dplyr::mutate(
    test_description = word(test_description_self, 1),
    size = size)



# Set colors for some
plot_data <- plot_data %>%
  dplyr::mutate(
    `Frequent Tools` = "Other",
    `Frequent Tools` = ifelse(substr(test_description, 1, 5) == "CAARS",
                              "CAARS", `Frequent Tools`),
    `Frequent Tools` = ifelse(substr(test_description, 1, 5) == "BAARS", 
                              "BAARS", `Frequent Tools`),
    `Frequent Tools` = ifelse(substr(test_description, 1, 4) == "ASRS", 
                              "ASRS", `Frequent Tools`),
    `Frequent Tools` = ifelse(substr(test_description, 1, 4) == "WURS", 
                              "WURS", `Frequent Tools`)
  )

plot_data %>%
  dplyr::group_by(test_description, `Frequent Tools`) %>%
  dplyr::summarise(n = dplyr::n()) %>%
  dplyr::arrange(desc(n)) %>%
  knitr::kable()

# 1. Define your colors in a named vector
# You must assign a color to every category, or the others will disappear/turn grey.
my_colors <- c(
  "ASRS"  = "#D55E00",    # Replace with your preferred color
  "CAARS" = "#0072B2",   # Replace with your preferred color
  "BAARS" = "#009E73",  # Replace with your preferred color
  "WURS"  = "#CC79A7",  # Replace with your preferred color
  "Other" = "#000000"   # The specific requirement
)

# 2. Plot
ggplot2::ggplot(
  data = plot_data, 
  aes(
    x = sensitivity,
    y = specificity,
    shape = Neurotypical_Only,
    size = size,
    color = `Frequent Tools`
  )
) +
  geom_point() +
  # 3. Add the manual scale
  scale_color_manual(values = my_colors) +
  xlab("Sensitivity (%)") +
  ylab("Specificity (%)") +
  ggrepel::geom_text_repel(
    aes(label = test_description), max.overlaps = 10, size = 5) +
  labs(
    shape = "Neurotypical only"
  ) +
  scale_size_continuous(
    name = "Size", # This sets the legend title
    breaks = c(50, 500, 1000), # Original untransformed values for legend
    labels = c("50", "500", "1000"), # Corresponding labels
    guide = "legend", # Explicitly request a legend
    # Set limits based on the *transformed* size values from your plot_data
    # This is crucial for the scale to match your actual plotted points
  ) + 
  theme(legend.position = "right") +
  xlim(c(0, 100)) + 
  ylim(c(0, 100))


d_test_description_np <- d %>%
  dplyr::select(
    ID, test_description_neuropsycho_tests, size
  ) %>% 
  dplyr::distinct() %>% 
  dplyr::mutate(
    test_description = word(test_description_neuropsycho_tests, 1)
  ) 

d_test_description_np %>%
  dplyr::group_by(test_description) %>%
  dplyr::summarise(n = dplyr::n()) %>%
  dplyr::arrange(desc(n)) %>%
  knitr::kable() %>% 
  print()

rm(plot_data)

# This is figure 6
cat("Neuropsychological \n Tests<p>")
plot_data <- d_ss_long %>%
  dplyr::filter(
    name == "Neuropsychological Test"
  ) %>%dplyr::inner_join(
    d_test_description_np
  ) %>%
  dplyr::mutate(test_description = word(test_description_neuropsycho_tests, 1)) 


# Set colors for some
plot_data <- plot_data %>%
  dplyr::mutate(
    `Frequent Tools` = "Other",
    `Frequent Tools` = 
      ifelse(substr(test_description, 1, 3) == "AQT", "AQT", `Frequent Tools`),
    `Frequent Tools` = 
      ifelse(substr(test_description, 1, 5) == "C-CPT", "C-CPT", `Frequent Tools`),
    `Frequent Tools` = 
      ifelse(substr(test_description, 1, 4) == "MOXO", "MOXO", `Frequent Tools`),
    `Frequent Tools` = 
      ifelse(substr(test_description, 1, 6) == "QbTest", "QbTest", `Frequent Tools`
      ),
    `Frequent Tools` = 
      ifelse(substr(test_description, 1, 5) == "Go-No", "Go-NoGo", `Frequent Tools`)
  )

my_colors <- c(
  "AQT"     = "#D55E00",    # Replace with your preferred color
  "C-CPT"   = "#0072B2",   # Replace with your preferred color
  "MOXO"    = "#009E73",  # Replace with your preferred color
  "QbTest"  = "#CC79A7",
  "Go-NoGo" = "#E69F00",
  "Other"   = "#000000"   # The specific requirement
)

plot_data %>% ggplot2::ggplot(
  aes(
    x = sensitivity, 
    y = specificity,
    shape = Neurotypical_Only, size = size,
    color = `Frequent Tools`)
) +
  geom_point() +
  scale_color_manual(values = my_colors) +
  xlab("Sensitivity (%)") + 
  ylab("Specificity (%)") +
  geom_text_repel(aes(label = test_description), max.overlaps = 10, size = 3) +
  labs(
    shape = "Neurotypical only"
  ) + 
  theme(legend.position = "right") +
  xlim(c(0, 100)) + 
  ylim(c(0, 100))



```

```{r auc}

AUC_vars <- 
  d %>% dplyr::select(
    starts_with("AUC") 
  ) %>%
  dplyr::select(-starts_with("AUC_CI")) %>%
  names()
AUC_vars

d <- d %>%
  dplyr::mutate(
    group = dplyr::case_when(
      Neurotypical == "Neurotypical" &
        Clinical != "Clinical" &
        Autism != "Autism" &
        Antisocial != "Antisocial" &
        Depression != "Depression" &
        Feigning != "Feigning" ~ "Neurotypical",
      (Clinical == "Clinical" |
         Autism == "Autism" |
         Antisocial == "Antisocial" |
         Depression == "Depression") &
        Neurotypical != "Neurotypical" &
        Feigning != "Feigning" ~ "Clinical",
      Neurotypical == "Neurotypical" & (
        Clinical == "Clinical" |
          Autism == "Autism" |
          Antisocial == "Antisocial" |
          Depression == "Depression" |
          Feigning == "Feigning" # Include Feigning here if needed for "Both"
      ) ~ "Both (or more)",
      TRUE ~ NA_character_
    )
  ) 



d_long_accuracy <- d %>%
  dplyr::select(
    accuracy_biomarker,
    accuracy_combination,
    accuracy_EEG,
    accuracy_neuroimaging,
    accuracy_neuropsycho_tests,
    accuracy_observational,
    accuracy_peer_rating,
    accuracy_self_report,
    group
  ) %>% 
  dplyr::filter(!is.na(group)) %>%
  pivot_longer(
    cols = starts_with("accuracy_"),
    names_to = "accuracy_type",
    values_to = "accuracy_value",
    names_prefix = "accuracy_"
  )%>% 
  dplyr::mutate(measure = "accuracy") %>%
  dplyr::rename_with(~ gsub("accuracy_", "", .x), starts_with("accuracy"))




d_long_AUC <- d %>%
  dplyr::select(
    starts_with("AUC"),
    group
  ) %>% 
  dplyr::mutate(
    AUC_neuropsycho_tests = as.numeric(AUC_neuropsycho_tests)
  ) %>% 
  dplyr::select(-starts_with("AUC_CI")) %>% 
  dplyr::filter(!is.na(group)) %>%
  pivot_longer(
    cols = starts_with("AUC_"),
    names_to = "AUC_type",
    values_to = "AUC_value",
    names_prefix = "AUC_"
  ) %>% 
  dplyr::mutate(
    AUC_value = ifelse(
      AUC_value < 1, AUC_value * 100, AUC_value
    )
  ) %>% 
  dplyr::mutate(measure = "AUC") %>%
  dplyr::rename_with(~ gsub("AUC_", "", .x), starts_with("AUC")) %>%     
  dplyr::filter(!is.na(value)) %>% 
  dplyr::filter(type != "feigningADHD")

d_long_both <- dplyr::bind_rows(
  d_long_accuracy, d_long_AUC
) %>% dplyr::filter(!is.na(value))

# Make labels nicer.

d_long_both <- d_long_both %>%
  dplyr::mutate(
    type = dplyr::case_when(
      type == "biomarker" ~ "Biomarker",
      type == "clinician_interview" ~ "Clinician\nTool",
      type == "combination" ~ "Combination",
      type == "neuroimaging" ~ "Neuroimaging",
      type == "observational" ~ "Observational",
      type == "neuropsycho_tests" ~ "Neuro-\npsychological",
      type == "peer_rating" ~ "Peer\nRating",
      type == "self_report" ~ "Self-Report",
      .default = type
    ),
    measure = ifelse(measure == "accuracy", "Accuracy", measure)
  )



d_long_both %>% dplyr::filter(!is.na(value)) %>%
  dplyr::rename(Group = group) %>%
  ggplot2::ggplot(
    aes(x = Group, y = value)
  )  + 
  geom_boxplot() +
  facet_grid(type ~ measure)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Figure 7
d_long_both %>% dplyr::filter(!is.na(value)) %>%
  dplyr::rename(Group = group) %>%
  ggplot2::ggplot(
    aes(x = Group, y = value)
  )  + 
  geom_boxplot() +
  facet_grid(measure ~ type)+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  labs(y = NULL)


d_long_both %>% dplyr::filter(!is.na(value)) %>%
  dplyr::rename(Group = group) %>%
  ggplot2::ggplot(
    aes(x = Group, y = value, color = measure)
  )  + 
  geom_boxplot() +
  facet_wrap(~ type) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

# Function to get Accuracy

```{r}


# Function to read CSV and select specific columns
read_adhd_data <- function(file_path) {
  
  # Read the CSV file
  d <- read.csv(file_path)
  
  # Select only the required columns
  clean_data <- d %>%
    select(n_ADHD, 
           sensitivity_self_report, 
           specificity_self_report,
           size, ID)
  
  return(clean_data)
}

########################### Usage example
accuracy <- read_adhd_data(data_location)
#############################

# Check the result
head(accuracy)


calculate_adhd_stats <- function(d) {
  
  processed_data <- d %>%
    mutate(
      # 1. Calculate Prevalence (P / Total)
      Prevalence = n_ADHD / size,
      
      # 2. Calculate (1 - Prevalence)
      One_Minus_Prevalence = 1 - Prevalence,
      
      # 3. Create cleaner columns for Sensitivity/Specificity for the formula
      Sensitivity = sensitivity_self_report,
      Specificity = specificity_self_report,
      
      # 4. Calculate Accuracy
      # Formula: (Sens * Prev) + (Spec * (1 - Prev))
      Accuracy = (Sensitivity * Prevalence) + (Specificity * One_Minus_Prevalence)
    )
  
  return(processed_data)
}
accuracy <- calculate_adhd_stats(accuracy)
head(accuracy)


accuracy <- accuracy %>%
  select(-Sensitivity, -Specificity)

# Create and save in one pipe chain
output_file <- "accuracy.html"


# Create and save
kableExtra::kbl(accuracy) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  save_kable(file = output_file)

```

## Program Summary of Findings Table

```{r prog_summary}
# Test: combination
# Outcome: Clinical_misdiagnosis



CreateProgSummary <- function(test_outcome_and_result) {
  
  if (test_outcome_and_result == "cost_self_report") {
    test_outcome_and_result <- "cost_self.report"
  }
  
  reverse_min_max <- 
    stringr::str_detect(test_outcome_and_result, "sensitivity") | 
    stringr::str_detect(test_outcome_and_result, "specificity") 
  
  print(test_outcome_and_result)
  
  if (test_outcome_and_result %in% 
      c(
        "admin_self_report", 
        "admin_neuropsycho_tests", 
        "cost_neuropsycho_tests",
        "concordance_self_report",
        "concordance_neuropsycho_tests",
        "kappa_neuropsycho_tests",
        "kappa_neuroimaging")
  ) {
    return(
      data.frame(
        test_outcome_and_result = test_outcome_and_result,
        contributing_studies = "Misnamed variable (probably doesn't matter?)",
        primary_results  = "Misnamed variable"
      )
    )
  }
  
  
  non_numeric_question <- !is.numeric(d[[test_outcome_and_result]]) 
  
  d_now <-
    d %>%
    dplyr::mutate(!!rlang::sym(test_outcome_and_result) := as.numeric(!!rlang::sym(test_outcome_and_result))) %>%
    dplyr::filter(!is.na(!!rlang::sym(test_outcome_and_result)))
  
  n <- nrow(d_now)
  min_value <- min(d_now[[test_outcome_and_result]])
  max_value <- max(d_now[[test_outcome_and_result]])
  
  min_id <- d_now[which(d_now[[test_outcome_and_result]] == min_value), "Refid"] %>% paste0(., collapse = ", ")
  max_id <- d_now[which(d_now[[test_outcome_and_result]] == max_value), "Refid"] %>% paste0(., collapse = ", ")
  
  
  contributing_studies <- (glue::glue(
    "{paste(d_now$ID)}")
  ) %>% as.character() %>% paste(., collapse = "; ")
  
  if(non_numeric_question) {
    contributing_studies <- primary_results <- "Warning: non-numeric result."
  } else {
    contributing_studies <- 
      glue::glue("{n} studies ({contributing_studies})")
    if (!reverse_min_max) {
      primary_results <- 
        glue::glue(
          "{min_value}(#{min_id}) to {max_value}(#{max_id})"
        )
    } else {
      primary_results <- 
        glue::glue(
          "{max_value}(#{max_id}) to {min_value}(#{min_id})"
        )
    }
    
  }
  
  
  return(
    data.frame(
      test_outcome_and_result = test_outcome_and_result,
      contributing_studies = contributing_studies,
      primary_results = primary_results))
}


kq_outcome <- c(
  "clinical_misdiagnosis",
  "sensitivity",
  "specificity",
  "admin",
  "kappa",
  "ICC",
  "cost",
  "concordance"
)

kq_index_test <- c(
  "combination",
  "self_report",
  "peer_rating",
  "neuropsycho_tests",
  "neuroimaging",
  "EEG",
  "biomarker",
  "observational",
  "clinician_interview",
  "clinician_tool",
  "feigningADHD"
)  

all_kqs <- 
  expand_grid(kq_index_test, kq_outcome ) %>% 
  dplyr::select(kq_outcome, kq_index_test) %>% 
  apply(., 1, paste0, collapse = "_")



res <- lapply(all_kqs, CreateProgSummary)

writexl::write_xlsx(dplyr::bind_rows(res), "adhd_adults_diagnosis_SoF.xlsx")

```

```{r}

```

## Sensitivity and Specificity Meta-Analysis

```{r}
#| results: asis
d$test_description_self_report <- word(d$test_description_self, 1)
d$test_description_peer_rating <- d$test_description_peer


# If you want to clean up any trailing spaces left behind:
d <- d %>%
  dplyr::mutate(
    study = gsub("\\{.*\\}", "", ID),
    study = trimws(study),
    study = ifelse(study == "van de Glind, 2013", "Van de Glind, 2013", study),
    test_description_self_report = test_description_self
  )


```

Need to loop through:

self_report peer_rating neuropsycho_tests neuroimaging clinician_interview combination biomarker EEG

```{r}
##| fig-width: 14
##| fig-height: 14

inv_logit <- function(x) { exp(x) / (1 + exp(x)) }
logit <- function(x) { log(x / (1 - x)) }

get_i2_un <- function(model) {
  W <- diag(1/model$vi)
  X <- model.matrix(model)
  P <- W - W %*% X %*% solve(t(X) %*% W %*% X) %*% t(X) %*% W
  v_bar <- (model$k - model$p) / sum(diag(P))
  
  i2 <- (model$tau2 / (sum(model$tau2) + v_bar)) * 100
  return(round(i2, 2))
}

plot_diagnostic_meta <- 
  function(
    d, diag_type_name, 
    true_pos, false_neg, 
    true_neg, false_pos,
    instrument_col,
    sens_reported,
    spec_reported
  ) {
    cat(glue::glue("<h2>{diag_type_name}</h2><br>"))
    d[[instrument_col]] <- stringr::word(d[[instrument_col]])
    
   list_dat <- CreateLongData(d = d, true_pos, true_neg, false_pos, false_neg)
   
   dat_sens_spec <- list_dat$dat_sens_spec 
   dat_long <- list_dat$dat_long
   
    # Find studies where calculated value of sens and spec differs from their calculation
    dat_sens_spec_discrepant <- dat_sens_spec %>%
      dplyr::filter(
        abs(round(sens_calculated) - !!sym(sens_reported) ) > 1 |
          abs(round(spec_calculated) - !!sym(spec_reported) ) > 1 
      )
    
    
    # 2. Run Meta-Analysis Model
    res <- metafor::rma.mv(
      yi, vi, mods = ~ outcome - 1, 
                           random = ~ outcome | study,
                           struct = "UN", data = dat_long
                           )
    output_text <- capture.output(print(res))
    cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
    
    i2_results <- get_i2_un(res)
    cat(glue::glue(
      "**I-squared for Sensitivity:** {i2_results[1]}%<p>")
    )    
    
    cat(glue::glue(
      "**I-squared for Specificity:** {i2_results[2]}%<p>")
    )    
    
    # 3. Setup Plotting Layout
    all_studies <- dat_long %>%
      distinct(study) %>%
      # Add the instrument label early so we can sort by it
      mutate(
        instrument_label = 
          d[[instrument_col]][match(study, d$study)]
      ) %>%
      # SORTING: Instrument (A-Z) and then Study (A-Z)
      # We arrange in ASCENDING order here...
      arrange(instrument_label, study) %>%
      # ...then we assign row_num so that the first item gets the HIGHEST row 
      # (putting it at the top of the plot)
      mutate(row_num = rev(row_number()))
    
    k_total <- nrow(all_studies)
    cex <- 0.6
    
    layout(matrix(c(1, 2), nrow = 1), widths = c(1.8, 1))
    
    
    # 4. Plot Sensitivity
    par(mar = c(5, 4, 3, 1))
    dat_sens_plot <- 
      all_studies %>% 
      left_join(filter(dat_long, outcome == "sens"), by = "study")
    
    metafor::forest(
      dat_sens_plot$yi, vi = dat_sens_plot$vi, slab = dat_sens_plot$study,
      transf = transf.ilogit,
      xlim = c(-1.2, 2.5), 
      ylim = c(-2, k_total + 3), 
      alim = c(0, 1),
      steps = 5,
      xlab = "Sensitivity",
      rows = all_studies$row_num, header = "Study", 
      main = paste(""), 
      refline = NA, cex = cex)
    
    text(-0.5, k_total + 2, "Tool", pos = 4, cex = cex, font = 2) 
    text(-0.5, all_studies$row_num, all_studies$instrument_label, 
         pos = 4, cex = cex
    )
    addpoly(res$beta[1], sei = res$se[1],
            row = -1, transf = transf.ilogit, mlab = "", 
            col = "red", cex = cex
    )
    
    # 5. Plot Specificity
    par(mar = c(5, 1, 3, 2))
    dat_spec_plot <- all_studies %>% 
      left_join(filter(dat_long, outcome == "spec"), by = "study")
    
    metafor::forest(
      dat_spec_plot$yi, 
      vi = dat_spec_plot$vi, 
      slab = NA, 
      transf = transf.ilogit, 
      xlab = "Specificity",
      xlim = c(-0.1, 2), 
      ylim = c(-2, k_total + 3), 
      rows = all_studies$row_num,
      alim = c(0, 1),
      steps = 5,
      header = "", main = "", 
      refline = NA, 
      cex = cex)
    
    addpoly(
      res$beta[2], 
      sei = res$se[2], 
      row = -1, 
      transf = transf.ilogit, 
      mlab = "", col = "red", cex = cex
    )
    
    cat("<h3>Discrepant Studies</h3><br>")
    
    cat("Discrepant studies are those where the value for 
        sensitivity and specificity that we calculate are > 1% different
        than the value that is in the paper.")
    if (nrow(dat_sens_spec_discrepant) == 0) {
      cat("No discrepant studies. <p>")
    } else {
      knitr::kable(dat_sens_spec_discrepant) %>% print()
    }
    
    
    
    ############### Neurotypical only
    cat("<h3>Neurotypical Only</h3><p>")
    
    dat_long$neurotypical_mod <-
      dat_long$Neurotypical == "Neurotypical"
    if (length(unique(dat_long$neurotypical_mod)) == 1) {
      cat("No variation in neurotypical - comparison not progressing.")
    } else {
      res_neurotypical <- metafor::rma.mv(
        yi, vi, 
        mods = ~ neurotypical_mod:outcome - 1,
        random = ~ outcome | study,
        struct = "UN", data = dat_long
      )

    
      output_text <- capture.output(print(res_neurotypical))
      cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
      
      results_tab <- as.data.frame(summary(res_neurotypical)$beta)
      results_tab$ci.lb <- res_neurotypical$ci.lb
      results_tab$ci.ub <- res_neurotypical$ci.ub
        
      # Apply the inverse logit: exp(x) / (1 + exp(x))
      results_transformed <- results_tab %>%
        mutate(
          Estimate_Prob = plogis(V1),
          Lower_CI = plogis(ci.lb),
          Upper_CI = plogis(ci.ub)
        ) %>%
        select(Estimate_Prob, Lower_CI, Upper_CI)
      
      
      print(knitr::kable(results_transformed, digits = 3))
      
      cat("Test of difference in sensitivity for neurotypical vs not<p>")
      output_text <- 
        capture.output(print(anova(res_neurotypical, L = c(-1, 1, 0, 0))))
      cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
 
      cat("Test of difference in specificity for neurotypical vs not<p>")
      output_text <- 
        capture.output(print(anova(res_neurotypical, L = c(0, 0, -1, 1))))
      cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
     }
    rm(res_neurotypical)
    ########## End neurotypical only
    
    ########## co-N/A vs (co-Anxiety, co-Autism, co-Depression, co-ODD, co-Other, co-SUD)
    cat("<h3>Comorbiditises Only</h3><p>")
    cat("Compare co-NA studies with any other comborbidity. <p>")
    
    dat_long <- CreateLongData(
      d, true_pos, true_neg, false_pos, false_neg)[[1]]
    
    d_comorbids <- d %>%
      dplyr::mutate(
        coNA = co.N.A == "co-N/A",
        has_comorbidity = (
          co.Anxiety == "co-Anxiety" |
          co.Autism == "co-Autism" |
          co.Depression == "co-Depression" |
          co.OCD == "co-OCD" |
          co.Other == "co-Other" |
          co.SUD ==  "co-SUD")
        ) %>%
      dplyr::filter(has_comorbidity | coNA) %>%
      dplyr::mutate(
        coNA = ifelse(is.na(coNA), FALSE, coNA),
        has_comorbidity  = ifelse(is.na(has_comorbidity ), FALSE, has_comorbidity )
      ) %>% 
      # join to long data
      dplyr::select(ID, has_comorbidity) %>%
      dplyr::full_join(
        dat_long, by = "ID"
      ) %>%
      dplyr::filter(!is.na(outcome))
    
      res_comorbidity <- metafor::rma.mv(
        yi, vi, 
        mods = ~ has_comorbidity:outcome - 1,
        random = ~ outcome | study,
        struct = "UN", data = d_comorbids
      )
    output_text <- capture.output(print(res_comorbidity))
    cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
    cat("Test of difference in sensitivity for comorbidity vs not<p>")
    
    output_text <- 
      output_text <- tryCatch({
        capture.output(print(anova(res_comorbidity, L = c(-1, 1, 0, 0))))
      }, error = function(e) {
        return(NA)
      })
    cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")
    
    cat("Test of difference in specificity for comorbidity vs not<p>")
    output_text <- 
      output_text <- tryCatch({
        capture.output(print(anova(res_comorbidity, L = c(0, 0, -1, 1))))
      }, error = function(e) {
        return(NA)
      })
    cat("```\n", paste(output_text, collapse = "\n"), "\n```\n", sep = "")     
    

    
    
  }




```

```{r}
#| results: asis
#| ##| fig-width: 14
##| fig-height: 14

#| 
# Define the categories you want to loop through

for (category in categories) {
  # Dynamically construct column names
  tp <- paste0("true_positive_", category)
  fn <- paste0("false_negative_", category)
  tn <- paste0("true_negative_", category)
  fp <- paste0("false_positive_", category)
  inst <- paste0("test_description_", category)
  sens_reported <- paste0("sensitivity_", category)
  spec_reported <- paste0("specificity_", category)
  
  
  # Generate the plot
  plot_diagnostic_meta(
    d = d, 
    diag_type_name = category, 
    true_pos = tp, 
    false_neg = fn, 
    true_neg = tn, 
    false_pos = fp, 
    instrument_col = inst,
    sens_reported,
    spec_reported
  )
}

```
